Title here

### 2016-12-06 portfolio/text/ms.Rmd
Edit results of commercial portfolio paper

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort (Fig. S\ref{fig:fe}),
specializing (decreasing species diversity) tends to be associated with
increased revenue (`r g2_dens`% probability; Fig. \ref{fig:within}). This is
particularly clear for permits where individuals tend to specialize on sockeye
salmon: individuals with setnet permits for salmon in Prince William Sound, Cook
Inlet, Kodiak, Bristol Bay, or the Alaska Peninsula experience a ~1.5% increase
in revenue for a 1% decrease in fished species diversity (Fig.
\ref{fig:within}B). The converse is also usually true --- generalizing tends to
be associated with lower expected revenue after accounting for fishing effort
(i.e. Fig. \ref{fig:within}A and \ref{fig:within}B are near mirror images left
to right). This specializing benefit for revenue is only apparent *after*
accounting for fishing effort. Given that fishing for more species tends to be
associated with increased fishing effort, generalizing tends to be associated
with higher revenue when not standardizing for fishing effort (Fig. S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) an
individual's fished species diversity within the constraints of a permit set
tends to be associated with greater expected variability or uncertainty in
year-to-year revenue (Fig. \ref{fig:within} strategies above 0; Fig.
S\ref{fig:fe}). This effect was strongest for individuals with a halibut
longline permit or halibut and sablefish longline permits. Individuals with
these strategies experienced ~2% increase in standardized variability for a 1%
change in fished species diversity (Fig. \ref{fig:within}). Fished species
diversity levels above one for these permits is primarily due to bycatch.

The Alaskan halibut and sablefish fisheries were "rationalized" in 199X --- they
switched from XX to an individual fishery quota (IFQ) system. We refit our
models allowing all effects to vary separately before and after 1995 for
strategies involving these permits (i.e. treating them as separate strategies).
The introduction of IFQs reduced variability by ~25% (XX--XX 95% CI) for
individuals with only a halibut or sablefish permit (Fig. S\ref{fig:ifq}A). For
most strategies, the effect of increased revenue variability associated with
changing fished species diversity became stronger after the introduction of IFQs
(Fig. S\ref{fig:ifq}B). This was especially true for individuals fishing only
halibut or sablefish (Fig. S\ref{fig:ifq}B).

>>>>

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort (Fig. S\ref{fig:fe}),
specializing (decreasing species diversity) tends to be associated with
increased revenue (~0.5% increased revenue per 1% decrease in species diversity
on average or TODO ... `r g2_dens`% probability; Fig. \ref{fig:within}). This is
particularly clear for permits where individuals tend to specialize on sockeye
salmon. For example, individuals with setnet permits for salmon in Prince
William Sound, Cook Inlet, Kodiak, Bristol Bay, or the Alaska Peninsula target
primarily sockeye salmon and experience a ~1.5% increase in revenue for a 1%
decrease in fished species diversity (Fig. \ref{fig:within}B). The converse is
also usually true --- generalizing tends to be associated with lower expected
revenue after accounting for fishing effort (i.e. Fig. \ref{fig:within}A and
\ref{fig:within}B are near mirror images left to right). This benefit of
specializing is only apparent after accounting for fishing effort. Given that
fishing for more species tends to be associated with increased fishing effort
(fishing more days), generalizing tends to be associated with higher revenue
when not standardizing for days finished (Fig. S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) an
individual's fished species diversity from year-to-year within the constraints
of a permit set tends to be associated with greater expected variability or
uncertainty in year-to-year revenue (Fig. \ref{fig:within} strategies above 0;
Fig. S\ref{fig:fe}). This effect was strongest for individuals with a halibut
longline permit or halibut and sablefish longline permits. Individuals with
these strategies experienced ~2% increase in standardized variability for a 1%
change in fished species diversity (Fig. \ref{fig:within}). Levels of fished
species diversity levels above one for these permits are primarily due to
bycatch.

The Alaskan halibut and sablefish fisheries were converted to an individual
fishery quota (IFQ) system in 1994. This catch share system... TODO. We refit
our models allowing all permit-level effects to vary separately before and after
the introduction of IFQs for strategies involving halibut and sablefish permits.
The introduction of IFQs reduced variability by ~25% (XX--XX 95% CI) for
individuals with only halibut or sablefish permits (Fig. S\ref{fig:ifq}A).
Furthermore, for most strategies, the effect of increased revenue variability
associated with changing species diversity became stronger after the
introduction of IFQs (Fig. S\ref{fig:ifq}B). This was especially true for
individuals fishing only halibut or sablefish and less so for individuals
combining halibut or sable fish with a salmon permit (Fig. S\ref{fig:ifq}B).
